---
title: "Code"
output: html_document
date: "2025-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("Functions.R")
```


# Testing


Treatment effects stuffs - single stage only

```{r}
theta1 <- 0
sigma <- 22
lambda <- 0.5
n <- 200

hat_theta1 <- rnorm(1, mean = theta1, sd = (4*sigma^2)/(lambda*n))
hat_theta1



theta2 <- 10
hat_theta2 <- rnorm(1, mean = theta2, sd = (4*sigma^2)/((1-lambda)*n))
hat_theta2



theta3 <- lambda*theta1 + (1-lambda)*theta2
hat_theta3 <- rnorm(1, mean = theta3, sd = (4*sigma^2)/n)
hat_theta3



```

## Stage 1:

```{r}
tau <- 0.5
lambda <- 0.5
n <- 200
sigma <- 22

theta1 <- 0
theta2 <- 10
########

theta3 <- lambda*theta1 + (1-lambda)*theta2

hat_theta1_1 <- rnorm(1, mean = theta1, sd = sqrt((4*sigma^2)/(tau*lambda*n)))
hat_theta2_1 <- rnorm(1, mean = theta2, sd = sqrt((4*sigma^2)/(tau*(1-lambda)*n)))
hat_theta3_1 <- rnorm(1, mean = theta3, sd = sqrt((4*sigma^2)/(tau*n)))
```



## Stage 2:

### No Enrichment:

```{r}
hat_theta1_2 <- rnorm(1, mean = theta1, sd = sqrt((4*sigma^2)/((1-tau)*lambda*n)))
hat_theta2_2 <- rnorm(1, mean = theta2, sd = sqrt((4*sigma^2)/((1-tau)*(1-lambda)*n)))
hat_theta3_2 <- rnorm(1, mean = theta3, sd = sqrt((4*sigma^2)/((1-tau)*n)))
```

### Enrichment:

```{r}
hat_theta1_2_enrich <- rnorm(1, mean = theta1, sd = sqrt((4*sigma^2)/((1-tau)*n)))
```










```{r}
# Do a trial
n <- 200
lambda <- 0.5
tau <- 0.5
sigma <- 22
theta1 <- 0
theta2 <- 10
```









Try to make it into data frames for vector calcs

```{r}
library(tidyverse)
```

```{r}
theta3 <- lambda * theta1 + (1 - lambda) * theta2
  
# Simulate the trial
hat_theta1_1 <- rnorm(5, mean = theta1, sd = sqrt((4*sigma^2)/(tau*lambda*n)))
hat_theta2_1 <- rnorm(5, mean = theta2, sd = sqrt((4*sigma^2)/(tau*(1-lambda)*n)))
hat_theta3_1 <- rnorm(5, mean = theta3, sd = sqrt((4*sigma^2)/(tau*n)))
  
dat <- data.frame(
  stage = "Stage 1",
  hat_theta1_1 = hat_theta1_1,
  hat_theta2_1 = hat_theta2_1,
  hat_theta3_1 = hat_theta3_1
)
dat
```
```{r}
# Add z-values and p-values to the data frame

dat <- dat %>%
  mutate(
    z1_1 = (sqrt(lambda*tau*n)*hat_theta1_1)/(2*sigma),
    z3_1 = (sqrt(tau*n)*hat_theta3_1)/(2*sigma),
    p1_1 = 1 - pnorm(z1_1),
    p3_1 = 1 - pnorm(z3_1),
    p_13_1 = simes_method(p1_1, p3_1)
  )


dat
```




STAGE 2

```{r}
dat2 <- data.frame(
    stage = "Stage 2",
    hat_theta1_2 = rnorm(5, mean = theta1, sd = sqrt((4*sigma^2)/((1-tau)*lambda*n))),
    hat_theta2_2 = rnorm(5, mean = theta2, sd = sqrt((4*sigma^2)/((1-tau)*(1-lambda)*n))),
    hat_theta3_2 = rnorm(5, mean = theta3, sd = sqrt((4*sigma^2)/((1-tau)*n)))
  )
dat2
```
```{r}
dat2 <- dat2 %>%
  mutate(
    z1_2 = (sqrt((1-tau)*lambda*n)*hat_theta1_2)/(2*sigma),
    z3_2 = (sqrt((1-tau)*n)*hat_theta3_2)/(2*sigma),
    p1_2 = 1 - pnorm(z1_2),
    p3_2 = 1 - pnorm(z3_2),
    p_13_2 = simes_method(p1_2, p3_2),
    enrich = rep(FALSE, 5)
  )
dat2
```

```{r}
dat2e <- data.frame(
    stage = "Stage 2",
    hat_theta1_2 = rnorm(5, mean = theta1, sd = sqrt((4*sigma^2)/((1-tau)*n)))
  )
dat2e
```
```{r}
dat2e <- dat2e %>%
  mutate(
    z1_2 = (sqrt((1-tau)*n)*hat_theta1_2)/(2*sigma),
    p1_2 = 1 - pnorm(z1_2),
    p_13_2 = p1_2,
    enrich = rep(TRUE, 5)
  )
dat2e
```



```{r}
dat_full <- bind_rows(dat, dat2, dat2e)
dat_full
```

```{r}
dat_full <- dat_full %>%
  mutate(
    P_13_1 = simes_method(p1_1, p3_1)
  )

dat_full
```





```{r}
dat <- StageOne(n_sim = 5, n = 200, lambda = 0.5, tau = 0.5, sigma = 22, theta1 = 0, theta2 = 10)
dat
```



col enrich - t or f

ideally do it without if else

reorder, group all t and all f

get num for each

use as num sim for stage 2 for each



```{r}
dat <- dat %>%
  arrange(
    enrich
  )
dat
```

```{r}
num_enrich <- sum(dat$enrich)
num_not <- nrow(dat) - num_enrich


no_en <- StageTwo_NoEnrich(num_not, n = 200, lambda = 0.5, tau = 0.5, sigma = 22, theta1 = 0, theta2 = 10)

en <- StageTwo_Enrich(num_enrich, n = 200, tau = 0.5, sigma = 22, theta1 = 0)


dat2 <- bind_rows(no_en, en)
dat2
```
```{r}
dat_full <- bind_cols(dat, dat2)
dat_full
```

Now we need to find the combined z and p values

```{r}
ws_no <- weights(lambda, tau)
ws_en <- weights(lambda, tau)

dat_full_no <- dat_full %>%
  filter(enrich == FALSE)

dat_full_en <- dat_full %>%
  filter(enrich == TRUE)


dat_full_no <- dat_full_no %>%
  mutate(
    z1_c = win(z1_1, z1_2, ws_no$w1, ws_no$w2),
    z3_c = win(z3_1, z3_2, ws_no$w1, ws_no$w2),
    z13_c = win_p(p_13_1, p_13_2, ws_no$w1, ws_no$w2),
    p1_c = 1 - pnorm(z1_c),
    p3_c = 1 - pnorm(z3_c),
    p13_c = 1 - pnorm(z13_c)
  )

dat_full_en <- dat_full_en %>%
  mutate(
    z1_c = win(z1_2, z1_2, ws_en$w1, ws_en$w2),
    z13_c = win_p(p_13_2, p_13_2, ws_en$w1, ws_en$w2),
    p1_c = 1 - pnorm(z1_c),
    p13_c = 1 - pnorm(z13_c)
  )


dat_full_combined <- bind_rows(dat_full_no, dat_full_en)
dat_full_combined
```


```{r}
dat_full_combined <- Comb(dat_full, lambda, tau)
dat_full_combined
```



So the full trial can be done by:
```{r}
library(tidyverse)
n <- 200
lambda <- 0.5
tau <- 0.5
sigma <- 22
theta1 <- 0
theta2 <- 10
n_sim <- 10^4


trial <- Trial(n_sim, n, lambda, tau, sigma, theta1, theta2)

trial
```


```{r}
trial %>%
  summarise(
    reject_13_c = mean(p13_c < 0.05),
    reject_1_c = mean(p1_c < 0.05),
    reject_3_c = mean(p3_c < 0.05)
  )
```


```{r}
# Power of test


trial %>%
  select(p13_c, p1_c, p3_c) %>%
  mutate(any_reject = if_any(everything(), ~ .x < 0.05)) %>%
  summarise(power = mean(any_reject))

```
```{r}
n <- 200
lambda <- 0.5
tau <- 0.5
sigma <- 13
theta1 <- 10
theta2 <- 10
n_sim <- 10^4


trial <- Trial(n_sim, n, lambda, tau, sigma, theta1, theta2)


trial %>%
  summarise(
    theta_3 = lambda * theta1 + (1 - lambda) * theta2,
    prob_only_H1 = mean(p1_c < 0.025 & p13_c < 0.025 & p3_c >= 0.025),
    prob_only_H3 = mean(p3_c < 0.025 & p13_c < 0.025 & p1_c >= 0.025),
    prob_only_Both = mean(p3_c < 0.025 & p13_c < 0.025 & p1_c < 0.025)
  )
```


```{r}
trial %>%
  summarise(
    theta_3 = lambda * theta1 + (1 - lambda) * theta2,
    prob_H1 = mean(p1_c < 0.025 & p13_c < 0.025),
    prob_H3 = mean(p3_c < 0.025 & p13_c < 0.025),
    FWER = mean((p1_c < 0.025 & p13_c < 0.025) | (p3_c < 0.025 & p13_c < 0.025)),
    FWER2 = mean((p1_c < 0.025 & p13_c < 0.025 & p3_c >= 0.025) | (p3_c < 0.025 & p13_c < 0.025 & p1_c >= 0.025))
  )
```

```{r}
trial %>%
  summarise(
    H13_only = mean(p1_c >= 0.025 & p13_c < 0.025 & p3_c >= 0.025),
    H13 = mean(p13_c < 0.025)
  )
```


oooooooooooooooooooooooooooooooooooooooooooooooooooo


## Bayesian


```{r}
n <- 200
lambda <- 0.5
tau <- 0.5
sigma <- 13

n_sim <- 10^4



theta1 <- rnorm(n_sim, mean = 10, sd = sigma)
theta2 <- rnorm(n_sim, mean = 0, sd = sigma)



trial <- Trial(n_sim, n, lambda, tau, sigma, theta1, theta2)


trial %>%
  summarise(
    theta_3 = lambda * theta1 + (1 - lambda) * theta2,
    prob_only_H1 = mean(p1_c < 0.025 & p13_c < 0.025 & p3_c >= 0.025),
    prob_only_H3 = mean(p3_c < 0.025 & p13_c < 0.025 & p1_c >= 0.025),
    prob_only_Both = mean(p3_c < 0.025 & p13_c < 0.025 & p1_c < 0.025)
  )
```

